A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
Modified latex.
Minor modifications to paper.

\section{Related Work}
\label{sec:reclated_work}

@@

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}

The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

@@

>>>>

% \section{Related Work}
% \label{sec:reclated_work}

@@

An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:

\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information. For this project we will be collecting data from Twitter using Twitter Streaming APIs. We collected tweets from [xxxx] users. To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users. We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.

\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. This is the central module that detects crowds of different types - communication, content, geo-graphical, etc. In this project we will be discovering crowds based on communication only. The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}. Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.

\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework. It can appear both before and after the grouper module depending upon its funcationality. In the figure we have showed the module appear before grouper only. When the module appears before the grouper, it is used to weed out information unnecessary for the grouper. For example in case of crowd detection, it remove information like spam messages. When the module appears after the grouper, it cleans the data generated by the grouper. For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees. 
The module can also have additional function like search.

% \begin{itemize}
%   \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information. For this project we will be collecting data from Twitter using Twitter Streaming APIs.
%   \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
%   \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
%   \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection. The API will return crowds, users, and their tweets.
% \end{itemize}

% \begin{itemize}
%   \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
%    \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
%    \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
% \end{itemize}

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}
The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

@@

{\scriptsize
 \bibliographystyle{abbrv}
 \bibliography{sigproc}
}
\balancecolumns % GM July 2000
